Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-12-31 manuscript.tex
20161231

\begin{abstract}
This paper presents a novel adaptive dynamic sliding mode scheme for the deployment of the tethered satellite system. To overcome the limited inputs of the dynamic model, a new scalable dimensionless transformation and strictly bounded terms are designed, which guarantee the existence of the ratio between limited inputs and command signals. The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain. The stability analysis indicates that this measure can eliminate the uncertainty caused by the input limitation and guarantee the asymptotically stability of the deployment dynamics. Finally, numerical simulations are presented to verify the effectiveness of the proposed control laws.
\end{abstract}
\begin{keyword}
Tethered satellite system;  Sliding mode control;  Input limitation; Adaptive control
\end{keyword}
\end{frontmatter}
\section{Introduction}
The deployment is the key technology of the space tethered satellite system (TSS)~\cite{wen2008advances,yousefian2015anti}, which supports various applications for space explorations and scientific researches, such as space debris removals, space elevators, satellite de-orbits and the tethered space robots~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,Huang2016Impact,Huang2016,Huang2016416,Huang2016171,Huang20161985}. Many international space research institutes have launched orbital, suborbital and ground experiments, such as TSS-1R, SEDS, MAST and YES2, in an effort to verify the feasibility of the proposed theoretical and simulation schemes for the deployment of the TSS~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}. These experimental results intensively help researchers proceed to promote advanced mechanics, kinetic and control studies, to tackle the future challenges of space activities~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line,Xu2016Hybrid}.

@@

\frac{\rm{d}}{\rm{d}\it{t}}F(t) = \delta\varphi \bm S_{r2}^T K_1\rm{e}\it{^{-2K_1^{-1}F^{-1}(t)}}\mathbf{sign}(\bm S_{r2})

@@

The simulation results of the deployment dynamics subjected to uncertainties are exhibited from Fig~\ref{fig:7} to Fig~\ref{fig:10}. In Fig~\ref{fig:7}, although there exist parametric uncertainties compared with the dynamics in Figs~\ref{fig:3}-\ref{fig:6}, QST-SMC still performs the deployment with the shortest rise time and the minimum overshoot among the three methods, and the tether is deployed to the desired position at about 8 $rad$ by observing the dynamics of the in-plane and out-of-plane angles from Fig~\ref{fig:9}. In addition, the result in Fig~\ref{fig:10} shows that the tension falls in the reasonable region, and meanwhile the chattering of the input in the stable status is reduced by utilizing the boundary layer technique. \textcolor{red}{Fig.~\ref{fig:11} shows the in-plane and out-of-plane thruster forces. From the results, we can find that all the forces are reasonable and limited in the boundary, and have less chattering by using the boundary layer technique. The in-plane thruster force has the similar results like the tension, the chattering of which is almost eliminated in the final stage. The boundary layer doesn't work well on the out-of-plane thruster force, and it is easy to see that the crossing boundary layer happens a lot, which may be caused by the external disturbance and uncertainties. However the technique still represses the chattering to some extents. Hence we can say that the boundary layer technique can indeed improve the inputs and repress the chattering.} The control precisions in Figs~\ref{fig:7}-\ref{fig:9} are almost same to Figs~\ref{fig:3}-\ref{fig:6}, which means the loss of precision caused by the boundary layer technique is limited. Moreover, the simulation results show that the good performance of proposed controller and the suitable boundary layer thickness guarantee that the system state error converges to the small vicinity of origin, which is consistent with the analyses in Theorem~\ref{thm:boundary}. Hence, the robustness of the proposed control laws can guarantee the stability of the deployment subjected to parametric uncertainties and external disturbances.
\includegraphics[width=0.6\textwidth]{paper4_fig7_20161025.eps}
\caption{Length dynamics of the deployment subjected to uncertainties and disturbances}
\label{fig:7}
\includegraphics[width=0.6\textwidth]{paper4_fig8_20161025.eps}
\caption{Length rate dynamics of the deployment subjected to uncertainties and disturbances}
\label{fig:8}
\includegraphics[width=0.6\textwidth]{paper4_fig9_20161025.eps}
\caption{Swing dynamics of the deployment subjected to uncertainties and disturbances}
\label{fig:9}
\includegraphics[width=0.6\textwidth]{paper4_fig10_20161025.eps}
\caption{Tension produced by utilizing boundary layer technique}
\label{fig:10}
\includegraphics[width=0.6\textwidth]{paper4_response_20161230.eps}
\caption{Thruster force}
\label{fig:11}
\section{Conclusion}\label{sec:5}
In this paper, the proposed adaptive sliding mode control laws provide the deployment dynamics of the TSS with a simplified solution for the reaching phase, which ignores the nonlinear nature of the model, and the new dimensionless transformation subjected to the limited input guarantees the effectiveness of the auxiliary Lyapunov function with adaptive terms. The simulation results show that the proposed methods adjust the length of the tether and the swing dynamics as desired, although there exists the input limitation during the deployment. Also, the robustness to parametric uncertainties and external disturbances is verified reasonably. According to the results mentioned above, combining error dynamics design approach, adaptive approach and nonlinear sliding mode surface design technology may provide a further insight into regulation of the deployment dynamics of the TSS.
\section{Acknowledgment}
This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61673009, 61503101, 91438202).
\section{References}
\bibliography{paper4_ref}
\bibliographystyle{elsarticle-num}
\end{document}

>>>>

\begin{abstract}
This paper presents a novel adaptive dynamic sliding mode scheme for the deployment of the tethered satellite system. To overcome the limited inputs of the dynamic model, a new scalable dimensionless transformation and strictly bounded terms are designed, which guarantee the existence of the ratio between limited inputs and command signals. The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain. The stability analysis indicates that this measure can eliminate the uncertainty caused by the input limitation and guarantee the asymptotically stability of the deployment dynamics. Finally, numerical simulations are presented to verify the effectiveness of the proposed control laws.
\end{abstract}
\begin{keyword}
Tethered satellite system;  Sliding mode control;  Input limitation; Adaptive control
\end{keyword}
\end{frontmatter}
\section{Introduction}
The deployment is the key technology of the space tethered satellite system (TSS)~\cite{wen2008advances,yousefian2015anti}, which supports various applications for space explorations and scientific researches, such as space debris removals, space elevators, satellite de-orbits and the tethered space robots~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,Huang2016Impact,Huang2016,Huang2016416}, and involves control theory, communication science and mechanical science~\cite{Li2014,Huang2016171,Huang20161985}. Many international space research institutes have launched orbital, suborbital and ground experiments, such as TSS-1R, SEDS, MAST and YES2, in an effort to verify the feasibility of the proposed theoretical and simulation schemes for the deployment of the TSS~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}. These experimental results intensively help researchers proceed to promote advanced mechanics, kinetic and control studies, to tackle the future challenges of space activities~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line,Xu2016Hybrid}.

@@

\frac{\rm{d}}{\rm{d}\it{t}}F(t) = \delta\varphi \bm S_{r2}^T K_1\rm{e}\it{^{-2K_1^{-1}F^{-1}(t)}}\mathbf{sign}(\bm {S}_{r2})

@@

The simulation results of the deployment dynamics subjected to uncertainties are exhibited from Fig~\ref{fig:7} to Fig~\ref{fig:10}. In Fig~\ref{fig:7}, although there exist parametric uncertainties compared with the dynamics in Figs~\ref{fig:3}-\ref{fig:6}, QST-SMC still performs the deployment with the shortest rise time and the minimum overshoot among the three methods, and the tether is deployed to the desired position at about 8 $rad$ by observing the dynamics of the in-plane and out-of-plane angles from Fig~\ref{fig:9}. In addition, the result in Fig~\ref{fig:10} shows that the tension falls in the reasonable region, and meanwhile the chattering of the input in the stable status is reduced by utilizing the boundary layer technique. \textcolor{red}{Fig.~\ref{fig:11} shows the in-plane and out-of-plane thruster forces. From the results, we can find that all the forces are reasonable and limited in the boundary, and have less chattering by using the boundary layer technique. The thruster forces have the similar behaviors like the tension, and the chattering is almost eliminated in the final stage. Hence we can say that the boundary layer technique can indeed improve the inputs and repress the chattering.} The control precisions in Figs~\ref{fig:7}-\ref{fig:9} are almost same to Figs~\ref{fig:3}-\ref{fig:6}, which means the loss of precision caused by the boundary layer technique is limited. Moreover, the simulation results show that the good performance of proposed controller and the suitable boundary layer thickness guarantee that the system state error converges to the small vicinity of origin, which is consistent with the analyses in Theorem~\ref{thm:boundary}. Hence, the robustness of the proposed control laws can guarantee the stability of the deployment subjected to parametric uncertainties and external disturbances.
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{paper4_fig7_20161025.eps}
\caption{Length dynamics of the deployment subjected to uncertainties and disturbances}
\label{fig:7}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{paper4_fig8_20161025.eps}
\caption{Length rate dynamics of the deployment subjected to uncertainties and disturbances}
\label{fig:8}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{paper4_fig9_20161025.eps}
\caption{Swing dynamics of the deployment subjected to uncertainties and disturbances}
\label{fig:9}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{paper4_fig10_20161025.eps}
\caption{Tension produced by utilizing boundary layer technique}
\label{fig:10}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{paper4_response_20161230.eps}
\caption{Thruster force}
\label{fig:11}
\end{figure}
\section{Conclusion}\label{sec:5}
In this paper, the proposed adaptive sliding mode control laws provide the deployment dynamics of the TSS with a simplified solution for the reaching phase, which ignores the nonlinear nature of the model, and the new dimensionless transformation subjected to the limited input guarantees the effectiveness of the auxiliary Lyapunov function with adaptive terms. The simulation results show that the proposed methods adjust the length of the tether and the swing dynamics as desired, although there exists the input limitation during the deployment. Also, the robustness to parametric uncertainties and external disturbances is verified reasonably. According to the results mentioned above, combining error dynamics design approach, adaptive approach and nonlinear sliding mode surface design technology may provide a further insight into regulation of the deployment dynamics of the TSS.
\section{Acknowledgment}
This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61673009, 61503101, 91438202).
\section{References}
\bibliography{paper4_ref}
\bibliographystyle{elsarticle-num}
\end{document}
